A Hybrid Neutronics Method for Time-Dependent Control Rod Modeling in Molten Salt Reactors

### 2024-06-12 lit.tex
Remove large spacing after al.

Whether one couples separate single-physics software together or develops a multiphysics software
under a single numerical solver framework, multiphysics software for modeling \glspl{MSR} must
employ \textit{tight coupling schemes} to couple the neutronics and thermal-hydraulics governing
equations to capture the strong multiphysics interactions in transient \gls{MSR} simulations
accurately without resorting to very small time-steps \cite{aufiero_development_2014}. Tightly
coupled numerical models handle multiphysics interactions by either updating all state
variables simultaneously in one monolithic solve (\textit{full coupling}) or
iteratively updating all state variables (\textit{fixed point iterations})
until the solution converges in every timestep \cite{keyes_multiphysics_2013}.
Full coupling tends to be more computationally expensive because it combines
all physics equations into a single large system of equations to be solved
simultaneously. In contrast, fixed point iterations involve operator splitting to
separate the system of equations into smaller systems based on their associated
physics, solving smaller systems separately, and iteratively updating the state
variables until convergence. Fixed point iterative methods can be less
stable, less accurate, and have poorer
convergence rates since these methods make iterative corrections
without regard to potentially destabilizing modes introduced by the
multiphysics coupling \cite{keyes_multiphysics_2013}. In particular, Lindsay et al.
\cite{lindsay_introduction_2018} demonstrated the non-convergence of a multiphysics \gls{MSR}
model without delayed neutron precursors when using fixed point iterations. While fully coupled
schemes result in large systems of equations to solve, they can still outperform fixed point
iterative methods in some multiphysics problems through superior stability and convergence rates.
Conversely, proven techniques exist for improving the performance of fixed point iteration coupling
schemes for many relevant computational multiphysics research fields, including reactor analysis
\cite{ragusa_consistent_2009}. Fixed point iterative methods also allow for different temporal and
spatial discretization schemes to meet the requisite resolution of each
individual physics model.

In contrast to tight coupling schemes, \textit{loose coupling schemes}
solve each set of single-physics equations using state variable
data from the previous timestep without iterative corrections within every
timestep. Loosely coupled schemes are inappropriate for modeling \glspl{MSR},
given the strong coupling between neutronics and thermal-hydraulics.
Aufiero et al. \cite{aufiero_development_2014} demonstrated a loose coupling
approach that failed to reproduce the expected increase in reactor power
in an \gls{MSR} in response to a 150 pcm reactivity insertion. One rare use case for loose
coupling is pseudo-transient problems for converging a multiphysics system to steady state.

@@

In 2007, Krepel et al. \cite{krepel_dyn3d-msr_2007} extended the
\gls{LWR} nodal diffusion code DYN3D to account for \gls{DNP} drift and fission energy deposition
in the coolant for \gls{MSR} modeling. The extended DYN3D-MSR code also contains the FLOCAL
thermal-hydraulics model for coolant flow and conjugate heat transfer modeling. Their \gls{MSRE}
and \gls{MSBR} models consisted of homogeneous hexagonal nodes (mesh elements) for the nodal
diffusion calculation coupled to individual hexagonal unit cells comprising of graphite with
circular fuel channels in the center for the thermal-hydraulics calculations. They simulated
steady-state operation; start-up, coast-down, natural circulation transients; and an overcooling
transient in their \gls{MSRE} model. They also modeled steady-state operation and a single-channel
blockage transient in their \gls{MSBR} model.

At the \gls{TUD}, Kophazi et al.
\cite{kophazi_development_2009} coupled their in-house 3-D neutron diffusion software DALTON
\cite{boer_validation_2010} and thermal-hydraulics
software THERM to develop a 3-D \gls{MSR} simulation tool. They homogenized the heterogeneous fuel
and graphite region of the \gls{MSRE} for the neutronics calculation. They discretized the
homogeneous region into a Cartesian mesh and modeled a more accurate representation of the oblong
fuel channels in the graphite core matrix instead of the circular shape by Krepel et al.
\cite{krepel_dyn3d-msr_2007}.

Both efforts by Krepel et al. and Kophazi et al. showed good
agreement with \gls{MSRE} experimental data in their respective validation tests.
The researchers from \gls{TUD} continued in their approach of coupling separate single-physics
software to create \gls{MSR} simulation tools, as noted by the DALTON-HEAT
\cite{de_zwaan_static_2007} coupling to model the \gls{MSFR} \cite{fiorina_modelling_2014}. The
fast-spectrum \gls{MSFR} features a large pool of fuel salt in its single-channel design instead of
the \gls{MSRE}'s multi-channel design. As a result, the authors had to incorporate
multidimensional turbulent flow modeling to accurately model the complex flow profiles and
turbulence effects in the \gls{MSFR} during steady-state operation and transient scenarios. In a
later effort from the same institute, Tiberga et al. \cite{tiberga_discontinuous_2019} coupled
PHANTOM-$S_N$ and DGFlows for their participation in the CNRS benchmark study
\cite{tiberga_results_2020}. Developed at the \gls{CNRS}, the CNRS benchmark facilitates
code-to-code verification of \gls{MSR} multiphysics software \cite{aufiero_testing_2018}. Tiberga
et al. showed that their coupled PHANTOM-$S_N$/DGFlows software was consistent with
OpenFOAM-based \gls{MSR} simulation tools. Further details on their study and the CNRS benchmark
is available in Section \ref{sec:msr-vv}.

@@

More recently, Jaradat et al. \cite{jaradat_development_2021}
extended the 3-D $P_1$ and $SP_3$ nodal transport code PROTEUS-NODAL to support \gls{DNP} drift.
Yang et al. \cite{yang_development_2022} then developed a coupled simulation tool of PROTEUS-NODAL
and \gls{SAM}. They modeled the \gls{MSFR} on a 2-D axisymmetric geometry
and the \gls{MSRE} on a 3-D R-$\theta$-Z geometry with twelve 1-D flow channels. The \gls{SAM} flow
model relied on the algebraic mixing length model for turbulence modeling. Both results
reproduced the expected trends observed in published experimental and simulation data. However,
their 1-D flow models neglected complex turbulent flows expected in the \gls{MSFR}.

@@

Laureau et al.
\cite{laureau_transient_2017} developed a different technique called the
\gls{TFM} method by introducing additional time-dependence
operators to conventional fission matrices typically used to accelerate source
convergence in Monte Carlo neutronics calculations. The \gls{TFM} method
pre-calculates three \glspl{TFM} of the reactor system in Serpent. It
interpolates the matrix values during the actual transient calculations to
incorporate temperature-induced salt expansion and Doppler effects on the neutron cross sections
and, ultimately, the neutron flux. Laureau et al. opted to subcycle the neutronics calculations by
setting smaller timesteps than the thermal-hydraulics calculations
to take advantage of the differing physics timescales. They demonstrated load-following capability
and parametric studies of overcooling and reactivity insertion transients in the \gls{MSFR}.

Blanco \cite{blanco_neutronic_2020} took a more direct approach by
compiling Serpent as an internal \texttt{C}-based function within OpenFOAM's
\texttt{C++}-based framework. This approach reduced the amount of external data
transfers between Serpent and OpenFOAM as both software have access to shared
memory during runtime. Their integrated tool employs the Quasi-Static
method for transient neutronics calculations and runs Serpent Monte Carlo
calculations several times per timestep until convergence is reached.
Blanco demonstrated the Serpent-OpenFOAM tool on the CNRS benchmark specified by Tiberga et al.
\cite{tiberga_results_2020}.

@@

Another \gls{MSR} simulation approach involves developing inherently multiphysics software that
handle all multiphysics calculations and data transfer internally. Among earlier efforts, Nicolino
et al. \cite{nicolino_coupled_2008} and Zhang et al. \cite{zhang_development_2009} recognized the
need for more robust multiphysics coupling, acceleration techniques and internal data transfers
to reduce execution times. They each independently developed unnamed multiphysics simulation tools
and demonstrated their tools with non-moderated \gls{MSR} designs. Nicolino et al. presented one of
the first \gls{MSR} models with multi-dimensional flow, governed by the Navier-Stokes equation with
the Boussinesq approximation. They performed steady-state and transient calculations on a 2-D
axisymmetric model of the \gls{MOSART} reactor \cite{ignatiev_molten_2014}. Zhang et al. also
developed a similar 2-D axisymmetric solver, but they incorporated a $k$-$\epsilon$ turbulence
model and performed calculations on an unnamed pool-type \gls{MSR} design with graphite reflectors.
Both studies implemented the neutron diffusion model for neutronics modeling.
Later, Li et al. \cite{li_transient_2015} demonstrated the
steady-state and transient analysis capabilities of COUPLE, a neutronics and
thermal-hydraulics software, on a 2-D axisymmetric model of the \gls{MSFR}. COUPLE also solves the
neutron diffusion equations and the Navier-Stokes equations with the $k$-$\epsilon$ turbulence
model.

@@

Other institutes have dedicated significant development work towards
OpenFOAM-based \gls{MSR} simulation tools. Aufiero et al.
\cite{aufiero_development_2014} first introduced an OpenFOAM model developed
at \gls{PoliMi}. Their model implemented a neutron diffusion model and a
\gls{RANS}-based turbulence model under the incompressible flow assumption to demonstrate 2-D
and 3-D transient analyses of the \gls{MSFR}. Later advancements in the
\gls{PoliMi} solver include a fuel compressibility model with helium bubble
tracking to study fuel compressibility effects
\cite{cervi_development_2019} and an $SP_3$ neutron transport
model for improved neutronics calculations \cite{cervi_development_2019-1} in
the \gls{MSFR}. GeN-Foam is another OpenFOAM-based tool developed by Fiorina
et al. \cite{fiorina_gen-foam_2015} as a general reactor multiphysics solver
applicable to \glspl{MSR} and other reactor types. GeN-Foam features neutron
diffusion, $SP_3$, and $S_N$ neutronics models
\cite{fiorina_development_2016,fiorina_gen-foam_2015,fiorina_detailed_2019},
and thermo-mechanical modeling for reactor expansion effects. Using GeN-Foam,
Altahhan et al. \cite{altahhan_preliminary_2020} developed and optimized a
liquid-fuel \gls{MSR} design, while Shi \& Fratoni \cite{shi_gen-foam_2021}
simulated precursor drift effects in a homogenized \gls{MSRE} model. However, none of the
OpenFOAM-based tools have demonstrated the capability for time-dependent \gls{MSR} simulations
with explicit control rod modeling.

Finally, within the \gls{MOOSE} framework, simulation tools capable of modeling
\glspl{MSR} include Griffin \cite{abou-jaoude_coupled_2020}; and Moltres
\cite{lindsay_moltres_2017}\textemdash the subject of this work.
Griffin primarily tackles radiation transport problems, but the \gls{MOOSE}
framework facilitates multiphysics coupling with \gls{MOOSE}-based applications for other physics
such that all applications share the same data structure. This feature eliminates
computational costs from external data transfers and optionally allows for
\textit{fully coupled} calculations in which the application solves all physics
simultaneously. The mutual compatibility among different physics applications within the
\gls{MOOSE} framework simplifies the work required to couple
different physics solvers together to solve novel multiphysics problems. Similarly,
Moltres benefits from the highly-integrated cross-compatibility
within the ecosystem of \gls{MOOSE}-based applications. Abou-Jaoude et al.
\cite{abou-jaoude_coupled_2020} coupled Griffin with Pronghorn, another
\gls{MOOSE}-based application for advanced reactor thermal-hydraulics modeling, to
demonstrate several steady-state \gls{MSR} simulation capabilities defined in
the CNRS benchmark. Lindsay et al.
\cite{lindsay_introduction_2018} first demonstrated Moltres' \gls{MSR} modeling
capabilities on 2-D axisymmetric and 3-D Cartesian models of the \gls{MSRE} with
fixed velocity flow in a fully coupled neutronics and thermal-hydraulics simulations.
I later demonstrated some of Moltres' more recent developments through
modeling a 2-D axisymmetric model of the \gls{MSFR} for steady-state operation
and transient accident analysis \cite{park_advancement_2020}. The latter study
introduced looped \gls{DNP} flow, coupling the \gls{DNP} drift and temperature 
advection-diffusion to incompressible flow, and decay heat modeling
capabilities.

@@

The important multiphysics phenomena in \glspl{MSR} for model \gls{VV} are salt flow-induced
\gls{DNP} drift and the strong coupling between neutron flux and temperature advection-diffusion.
Delpech et al. \cite{delpech_benchmark_2003} published one of the first collaborative \gls{VV} work
for \gls{MSR} multiphysics modeling. Collaborators
from six institutions modeled \gls{MSRE} pump start-up, pump coast-down, and natural
circulation transients to assess and validate their models and codes for studying the effects of
salt flow on the reactivity and power. Given the wide range of neutronics methods, from
multidimensional Monte Carlo methods to zero-dimensional point reactor kinetics, some deviations
were observed between different codes. Nevertheless, all results generally agreed
with \gls{MSRE} experimental data from \gls{ORNL}.

As mentioned in Subsection \ref{sec:msr-tools}, Tiberga et al. \cite{tiberga_results_2020}
published the CNRS benchmark to verify \gls{MSR} simulation tools designed for
fast-spectrum \gls{MSR} modeling. In contrast with the multi-channel \gls{MSRE} and its derivative
designs, the CNRS benchmark has a 2 m$\times$2 m problem domain of homogeneous fuel salt mimicking
the large salt pool in fast-spectrum \gls{MSR} designs. The CNRS benchmark consists of three
phases: single-physics calculations in Phase 0, problems that gradually
introduce multiphysics coupling in Phase 1, and time-dependent perturbation problems in Phase
2. Thus, the benchmark provides a systematic approach to help code developers
identify sources of discrepancies that may otherwise be masked by error cancellation or other
dominant sources of discrepancies. The final steady-state and time-dependent problems involve
studying the effects of natural circulation and lid-driven flow on the reactivity and power output.
Aside from the problem specifications, Tiberga et al. also published the associated group
constant cross section data required by deterministic neutronics solvers to perform neutronics
calculations. Four institutions participated in the benchmarking exercise with neutron diffusion,
$SP_N$, and $S_N$-based solvers for the neutronics calculations. Their measured neutronics and
\gls{TH} parameters showed excellent agreement within up to 2.5\% discrepancy from their combined
average.

Neutronic benchmark studies of the \gls{MSRE} and the \gls{MSFR} by Fratoni et al.
\cite{fratoni_molten_2020} and Brovchenko et al. \cite{brovchenko_neutronic_2019} measured the
delayed neutron losses due to the decay of \glspl{DNP} flowing out of the active core region.
Fratoni et al. sought to establish a standard validation platform for \gls{MSR} neutronics
simulation tools with \gls{MSRE} experimental data for inclusion in the \gls{IRPhEP} handbook.
They characterized and validated a model of the \gls{MSRE} in the Monte Carlo particle transport
code Serpent. The \gls{MSFR} neutronics benchmark by Brovchenko et al. featured results
from multiple \gls{MSR} simulation tools by several collaborators. Their assessment found that
the choice of nuclear database for the cross sections and decay data has the most significant
impact on the neutronics results.

While these publications have addressed significant technical gaps, there is room to develop
further \gls{VV} benchmarks for multiphysics \gls{MSR} modeling. For instance, the
CNRS benchmark does not assess the loss of delayed neutrons due to the decay of \glspl{DNP} flowing
out of the active core region. This phenomenon is important as the delayed neutron fraction in the
core directly impacts the transient power response in unprotected accident scenarios. Meanwhile,
the neutronic benchmark studies by Fratoni et al. \cite{fratoni_molten_2020} and Brovchenko et al.
\cite{brovchenko_neutronic_2019} did not provide the standardized group constant data required by
most deterministic multiphysics \gls{MSR} simulation tools. Therefore, it is challenging to isolate
discrepancies arising from code implementations instead of discrepancies from using different
nuclear databases or stochastic uncertainties in Monte Carlo simulations. A suitable model
verification procedure for delayed neutron loss should ideally provide well-defined problems and
the necessary input data. It is also helpful to perform model verification studies on simpler
problems like the bare homogeneous problem domain in the CNRS benchmark before embarking on more
detailed validation studies that require accurate models of experimental setups.

@@

Podila et al. \cite{podila_cfd_2019} performed \gls{CFD} simulations of the
\gls{MSRE} core with six different turbulence models, namely a Spalart-Allmaras
model, two variants of the $k$-$\epsilon$ model, a $k$-$\omega$ model, and two
variants of \glspl{RSM}. While the turbulence models predicted widely differing near-wall
turbulence intensity distributions, their results showed small differences
in graphite and fuel temperatures among the different turbulence models. Ultimately, given
the lack of experimental data for model validation, the authors could compare between the
models, but they could not provide a definitive
assessment of the models' accuracies.

Amongst other \gls{MSR} simulation tools, the $k$-$\epsilon$ and $k$-$\omega$
turbulence models are the most commonly used models, as shown in published work
with COMSOL \cite{fiorina_modelling_2014}, OpenFOAM
\cite{aufiero_development_2014}, and \gls{TUD}'s in-house codes
\cite{fiorina_modelling_2014,tiberga_results_2020}. Fiorina et al.
\cite{fiorina_modelling_2014} compared the flow distribution from both models
in a 2-D axisymmetric \gls{MSFR} geometry. They observed that the $k$-$\omega$
model produced a more expansive recirculation zone near the outer wall, an additional
recirculation zone near the top wall, and significantly higher maximum
temperatures within the former recirculation zone.

In a recent study by
Laureau et al. \cite{laureau_unmoderated_2022}, the authors applied a \gls{DES} model to model
eddies in the \gls{MSFR}. Given the high computational costs required to obtain reasonably small
stochastic uncertainties from Monte Carlo calculations on arbitrarily varying temperature fields,
they developed a reduced-order model relating local reactivity feedback estimates to the nominal
temperature field to obtain the effective temperature field.
Additionally, they fixed the total
reactor power output to 3 GW to further reduce costs. With this multiphysics model, they found
that the pre-existing \gls{MSFR} model was prone to large power fluctuations of up to 7.5\% under
steady-state operation. Previous studies with lower-fidelity models, including the two-equation
models, failed to capture this effect due to the time-averaging assumption required in those
models. After replacing the large inlet pipes with multiple blade-like inlet channels in the
\gls{MSFR} model, they managed to reduce power fluctuations to 1.2\%.

>>>>

Whether one couples separate single-physics software together or develops a multiphysics software
under a single numerical solver framework, multiphysics software for modeling \glspl{MSR} must
employ \textit{tight coupling schemes} to couple the neutronics and thermal-hydraulics governing
equations to capture the strong multiphysics interactions in transient \gls{MSR} simulations
accurately without resorting to very small time-steps \cite{aufiero_development_2014}. Tightly
coupled numerical models handle multiphysics interactions by either updating all state
variables simultaneously in one monolithic solve (\textit{full coupling}) or
iteratively updating all state variables (\textit{fixed point iterations})
until the solution converges in every timestep \cite{keyes_multiphysics_2013}.
Full coupling tends to be more computationally expensive because it combines
all physics equations into a single large system of equations to be solved
simultaneously. In contrast, fixed point iterations involve operator splitting to
separate the system of equations into smaller systems based on their associated
physics, solving smaller systems separately, and iteratively updating the state
variables until convergence. Fixed point iterative methods can be less
stable, less accurate, and have poorer
convergence rates since these methods make iterative corrections
without regard to potentially destabilizing modes introduced by the
multiphysics coupling \cite{keyes_multiphysics_2013}. In particular, Lindsay et al.\
\cite{lindsay_introduction_2018} demonstrated the non-convergence of a multiphysics \gls{MSR}
model without delayed neutron precursors when using fixed point iterations. While fully coupled
schemes result in large systems of equations to solve, they can still outperform fixed point
iterative methods in some multiphysics problems through superior stability and convergence rates.
Conversely, proven techniques exist for improving the performance of fixed point iteration coupling
schemes for many relevant computational multiphysics research fields, including reactor analysis
\cite{ragusa_consistent_2009}. Fixed point iterative methods also allow for different temporal and
spatial discretization schemes to meet the requisite resolution of each
individual physics model.

In contrast to tight coupling schemes, \textit{loose coupling schemes}
solve each set of single-physics equations using state variable
data from the previous timestep without iterative corrections within every
timestep. Loosely coupled schemes are inappropriate for modeling \glspl{MSR},
given the strong coupling between neutronics and thermal-hydraulics.
Aufiero et al.\ \cite{aufiero_development_2014} demonstrated a loose coupling
approach that failed to reproduce the expected increase in reactor power
in an \gls{MSR} in response to a 150 pcm reactivity insertion. One rare use case for loose
coupling is pseudo-transient problems for converging a multiphysics system to steady state.

@@

In 2007, Krepel et al.\ \cite{krepel_dyn3d-msr_2007} extended the
\gls{LWR} nodal diffusion code DYN3D to account for \gls{DNP} drift and fission energy deposition
in the coolant for \gls{MSR} modeling. The extended DYN3D-MSR code also contains the FLOCAL
thermal-hydraulics model for coolant flow and conjugate heat transfer modeling. Their \gls{MSRE}
and \gls{MSBR} models consisted of homogeneous hexagonal nodes (mesh elements) for the nodal
diffusion calculation coupled to individual hexagonal unit cells comprising of graphite with
circular fuel channels in the center for the thermal-hydraulics calculations. They simulated
steady-state operation; start-up, coast-down, natural circulation transients; and an overcooling
transient in their \gls{MSRE} model. They also modeled steady-state operation and a single-channel
blockage transient in their \gls{MSBR} model.

At the \gls{TUD}, Kophazi et al.\
\cite{kophazi_development_2009} coupled their in-house 3-D neutron diffusion software DALTON
\cite{boer_validation_2010} and thermal-hydraulics
software THERM to develop a 3-D \gls{MSR} simulation tool. They homogenized the heterogeneous fuel
and graphite region of the \gls{MSRE} for the neutronics calculation. They discretized the
homogeneous region into a Cartesian mesh and modeled a more accurate representation of the oblong
fuel channels in the graphite core matrix instead of the circular shape by Krepel et al.\
\cite{krepel_dyn3d-msr_2007}.

Both efforts by Krepel et al.\ and Kophazi et al.\ showed good
agreement with \gls{MSRE} experimental data in their respective validation tests.
The researchers from \gls{TUD} continued in their approach of coupling separate single-physics
software to create \gls{MSR} simulation tools, as noted by the DALTON-HEAT
\cite{de_zwaan_static_2007} coupling to model the \gls{MSFR} \cite{fiorina_modelling_2014}. The
fast-spectrum \gls{MSFR} features a large pool of fuel salt in its single-channel design instead of
the \gls{MSRE}'s multi-channel design. As a result, the authors had to incorporate
multidimensional turbulent flow modeling to accurately model the complex flow profiles and
turbulence effects in the \gls{MSFR} during steady-state operation and transient scenarios. In a
later effort from the same institute, Tiberga et al.\ \cite{tiberga_discontinuous_2019} coupled
PHANTOM-$S_N$ and DGFlows for their participation in the CNRS benchmark study
\cite{tiberga_results_2020}. Developed at the \gls{CNRS}, the CNRS benchmark facilitates
code-to-code verification of \gls{MSR} multiphysics software \cite{aufiero_testing_2018}. Tiberga
et al.\ showed that their coupled PHANTOM-$S_N$/DGFlows software was consistent with
OpenFOAM-based \gls{MSR} simulation tools. Further details on their study and the CNRS benchmark
is available in Section \ref{sec:msr-vv}.

@@

More recently, Jaradat et al.\ \cite{jaradat_development_2021}
extended the 3-D $P_1$ and $SP_3$ nodal transport code PROTEUS-NODAL to support \gls{DNP} drift.
Yang et al.\ \cite{yang_development_2022} then developed a coupled simulation tool of PROTEUS-NODAL
and \gls{SAM}. They modeled the \gls{MSFR} on a 2-D axisymmetric geometry
and the \gls{MSRE} on a 3-D R-$\theta$-Z geometry with twelve 1-D flow channels. The \gls{SAM} flow
model relied on the algebraic mixing length model for turbulence modeling. Both results
reproduced the expected trends observed in published experimental and simulation data. However,
their 1-D flow models neglected complex turbulent flows expected in the \gls{MSFR}.

@@

Laureau et al.\
\cite{laureau_transient_2017} developed a different technique called the
\gls{TFM} method by introducing additional time-dependence
operators to conventional fission matrices typically used to accelerate source
convergence in Monte Carlo neutronics calculations. The \gls{TFM} method
pre-calculates three \glspl{TFM} of the reactor system in Serpent. It
interpolates the matrix values during the actual transient calculations to
incorporate temperature-induced salt expansion and Doppler effects on the neutron cross sections
and, ultimately, the neutron flux. Laureau et al.\ opted to subcycle the neutronics calculations by
setting smaller timesteps than the thermal-hydraulics calculations
to take advantage of the differing physics timescales. They demonstrated load-following capability
and parametric studies of overcooling and reactivity insertion transients in the \gls{MSFR}.

Blanco \cite{blanco_neutronic_2020} took a more direct approach by
compiling Serpent as an internal \texttt{C}-based function within OpenFOAM's
\texttt{C++}-based framework. This approach reduced the amount of external data
transfers between Serpent and OpenFOAM as both software have access to shared
memory during runtime. Their integrated tool employs the Quasi-Static
method for transient neutronics calculations and runs Serpent Monte Carlo
calculations several times per timestep until convergence is reached.
Blanco demonstrated the Serpent-OpenFOAM tool on the CNRS benchmark specified by Tiberga et al.\
\cite{tiberga_results_2020}.

@@

Another \gls{MSR} simulation approach involves developing inherently multiphysics software that
handle all multiphysics calculations and data transfer internally. Among earlier efforts, Nicolino
et al.\ \cite{nicolino_coupled_2008} and Zhang et al.\ \cite{zhang_development_2009} recognized the
need for more robust multiphysics coupling, acceleration techniques and internal data transfers
to reduce execution times. They each independently developed unnamed multiphysics simulation tools
and demonstrated their tools with non-moderated \gls{MSR} designs. Nicolino et al.\ presented one
of the first \gls{MSR} models with multi-dimensional flow, governed by the Navier-Stokes equation
with the Boussinesq approximation. They performed steady-state and transient calculations on a 2-D
axisymmetric model of the \gls{MOSART} reactor \cite{ignatiev_molten_2014}. Zhang et al.\ also
developed a similar 2-D axisymmetric solver, but they incorporated a $k$-$\epsilon$ turbulence
model and performed calculations on an unnamed pool-type \gls{MSR} design with graphite reflectors.
Both studies implemented the neutron diffusion model for neutronics modeling.
Later, Li et al.\ \cite{li_transient_2015} demonstrated the
steady-state and transient analysis capabilities of COUPLE, a neutronics and
thermal-hydraulics software, on a 2-D axisymmetric model of the \gls{MSFR}. COUPLE also solves the
neutron diffusion equations and the Navier-Stokes equations with the $k$-$\epsilon$ turbulence
model.

@@

Other institutes have dedicated significant development work towards
OpenFOAM-based \gls{MSR} simulation tools. Aufiero et al.\
\cite{aufiero_development_2014} first introduced an OpenFOAM model developed
at \gls{PoliMi}. Their model implemented a neutron diffusion model and a
\gls{RANS}-based turbulence model under the incompressible flow assumption to demonstrate 2-D
and 3-D transient analyses of the \gls{MSFR}. Later advancements in the
\gls{PoliMi} solver include a fuel compressibility model with helium bubble
tracking to study fuel compressibility effects
\cite{cervi_development_2019} and an $SP_3$ neutron transport
model for improved neutronics calculations \cite{cervi_development_2019-1} in
the \gls{MSFR}. GeN-Foam is another OpenFOAM-based tool developed by Fiorina
et al.\ \cite{fiorina_gen-foam_2015} as a general reactor multiphysics solver
applicable to \glspl{MSR} and other reactor types. GeN-Foam features neutron
diffusion, $SP_3$, and $S_N$ neutronics models
\cite{fiorina_development_2016,fiorina_gen-foam_2015,fiorina_detailed_2019},
and thermo-mechanical modeling for reactor expansion effects. Using GeN-Foam,
Altahhan et al.\ \cite{altahhan_preliminary_2020} developed and optimized a
liquid-fuel \gls{MSR} design, while Shi \& Fratoni \cite{shi_gen-foam_2021}
simulated precursor drift effects in a homogenized \gls{MSRE} model. However, none of the
OpenFOAM-based tools have demonstrated the capability for time-dependent \gls{MSR} simulations
with explicit control rod modeling.

Finally, within the \gls{MOOSE} framework, simulation tools capable of modeling
\glspl{MSR} include Griffin \cite{abou-jaoude_coupled_2020}; and Moltres
\cite{lindsay_moltres_2017}\textemdash the subject of this work.
Griffin primarily tackles radiation transport problems, but the \gls{MOOSE}
framework facilitates multiphysics coupling with \gls{MOOSE}-based applications for other physics
such that all applications share the same data structure. This feature eliminates
computational costs from external data transfers and optionally allows for
\textit{fully coupled} calculations in which the application solves all physics
simultaneously. The mutual compatibility among different physics applications within the
\gls{MOOSE} framework simplifies the work required to couple
different physics solvers together to solve novel multiphysics problems. Similarly,
Moltres benefits from the highly-integrated cross-compatibility
within the ecosystem of \gls{MOOSE}-based applications. Abou-Jaoude et al.\
\cite{abou-jaoude_coupled_2020} coupled Griffin with Pronghorn, another
\gls{MOOSE}-based application for advanced reactor thermal-hydraulics modeling, to
demonstrate several steady-state \gls{MSR} simulation capabilities defined in
the CNRS benchmark. Lindsay et al.\
\cite{lindsay_introduction_2018} first demonstrated Moltres' \gls{MSR} modeling
capabilities on 2-D axisymmetric and 3-D Cartesian models of the \gls{MSRE} with
fixed velocity flow in a fully coupled neutronics and thermal-hydraulics simulations.
I later demonstrated some of Moltres' more recent developments through
modeling a 2-D axisymmetric model of the \gls{MSFR} for steady-state operation
and transient accident analysis \cite{park_advancement_2020}. The latter study
introduced looped \gls{DNP} flow, coupling the \gls{DNP} drift and temperature 
advection-diffusion to incompressible flow, and decay heat modeling
capabilities.

@@

The important multiphysics phenomena in \glspl{MSR} for model \gls{VV} are salt flow-induced
\gls{DNP} drift and the strong coupling between neutron flux and temperature advection-diffusion.
Delpech et al.\ \cite{delpech_benchmark_2003} published one of the first collaborative \gls{VV} work
for \gls{MSR} multiphysics modeling. Collaborators
from six institutions modeled \gls{MSRE} pump start-up, pump coast-down, and natural
circulation transients to assess and validate their models and codes for studying the effects of
salt flow on the reactivity and power. Given the wide range of neutronics methods, from
multidimensional Monte Carlo methods to zero-dimensional point reactor kinetics, some deviations
were observed between different codes. Nevertheless, all results generally agreed
with \gls{MSRE} experimental data from \gls{ORNL}.

As mentioned in Subsection \ref{sec:msr-tools}, Tiberga et al.\ \cite{tiberga_results_2020}
published the CNRS benchmark to verify \gls{MSR} simulation tools designed for
fast-spectrum \gls{MSR} modeling. In contrast with the multi-channel \gls{MSRE} and its derivative
designs, the CNRS benchmark has a 2 m$\times$2 m problem domain of homogeneous fuel salt mimicking
the large salt pool in fast-spectrum \gls{MSR} designs. The CNRS benchmark consists of three
phases: single-physics calculations in Phase 0, problems that gradually
introduce multiphysics coupling in Phase 1, and time-dependent perturbation problems in Phase
2. Thus, the benchmark provides a systematic approach to help code developers
identify sources of discrepancies that may otherwise be masked by error cancellation or other
dominant sources of discrepancies. The final steady-state and time-dependent problems involve
studying the effects of natural circulation and lid-driven flow on the reactivity and power output.
Aside from the problem specifications, Tiberga et al.\ also published the associated group
constant cross section data required by deterministic neutronics solvers to perform neutronics
calculations. Four institutions participated in the benchmarking exercise with neutron diffusion,
$SP_N$, and $S_N$-based solvers for the neutronics calculations. Their measured neutronics and
\gls{TH} parameters showed excellent agreement within up to 2.5\% discrepancy from their combined
average.

Neutronic benchmark studies of the \gls{MSRE} and the \gls{MSFR} by Fratoni et al.\
\cite{fratoni_molten_2020} and Brovchenko et al.\ \cite{brovchenko_neutronic_2019} measured the
delayed neutron losses due to the decay of \glspl{DNP} flowing out of the active core region.
Fratoni et al.\ sought to establish a standard validation platform for \gls{MSR} neutronics
simulation tools with \gls{MSRE} experimental data for inclusion in the \gls{IRPhEP} handbook.
They characterized and validated a model of the \gls{MSRE} in the Monte Carlo particle transport
code Serpent. The \gls{MSFR} neutronics benchmark by Brovchenko et al.\ featured results
from multiple \gls{MSR} simulation tools by several collaborators. Their assessment found that
the choice of nuclear database for the cross sections and decay data has the most significant
impact on the neutronics results.

While these publications have addressed significant technical gaps, there is room to develop
further \gls{VV} benchmarks for multiphysics \gls{MSR} modeling. For instance, the CNRS benchmark
does not assess the loss of delayed neutrons due to the decay of \glspl{DNP} flowing out of the
active core region. This phenomenon is important as the delayed neutron fraction in the core
directly impacts the transient power response in unprotected accident scenarios. Meanwhile, the
neutronic benchmark studies by Fratoni et al.\ \cite{fratoni_molten_2020} and Brovchenko et al.\
\cite{brovchenko_neutronic_2019} did not provide the standardized group constant data required by
most deterministic multiphysics \gls{MSR} simulation tools. Therefore, it is challenging to isolate
discrepancies arising from code implementations instead of discrepancies from using different
nuclear databases or stochastic uncertainties in Monte Carlo simulations. A suitable model
verification procedure for delayed neutron loss should ideally provide well-defined problems and
the necessary input data. It is also helpful to perform model verification studies on simpler
problems like the bare homogeneous problem domain in the CNRS benchmark before embarking on more
detailed validation studies that require accurate models of experimental setups.

@@

Podila et al.\ \cite{podila_cfd_2019} performed \gls{CFD} simulations of the
\gls{MSRE} core with six different turbulence models, namely a Spalart-Allmaras
model, two variants of the $k$-$\epsilon$ model, a $k$-$\omega$ model, and two
variants of \glspl{RSM}. While the turbulence models predicted widely differing near-wall
turbulence intensity distributions, their results showed small differences
in graphite and fuel temperatures among the different turbulence models. Ultimately, given
the lack of experimental data for model validation, the authors could compare between the
models, but they could not provide a definitive
assessment of the models' accuracies.

Amongst other \gls{MSR} simulation tools, the $k$-$\epsilon$ and $k$-$\omega$
turbulence models are the most commonly used models, as shown in published work
with COMSOL \cite{fiorina_modelling_2014}, OpenFOAM
\cite{aufiero_development_2014}, and \gls{TUD}'s in-house codes
\cite{fiorina_modelling_2014,tiberga_results_2020}. Fiorina et al.\
\cite{fiorina_modelling_2014} compared the flow distribution from both models
in a 2-D axisymmetric \gls{MSFR} geometry. They observed that the $k$-$\omega$
model produced a more expansive recirculation zone near the outer wall, an additional
recirculation zone near the top wall, and significantly higher maximum
temperatures within the former recirculation zone.

In a recent study by
Laureau et al.\ \cite{laureau_unmoderated_2022}, the authors applied a \gls{DES} model to model
eddies in the \gls{MSFR}. Given the high computational costs required to obtain reasonably small
stochastic uncertainties from Monte Carlo calculations on arbitrarily varying temperature fields,
they developed a reduced-order model relating local reactivity feedback estimates to the nominal
temperature field to obtain the effective temperature field.
Additionally, they fixed the total
reactor power output to 3 GW to further reduce costs. With this multiphysics model, they found
that the pre-existing \gls{MSFR} model was prone to large power fluctuations of up to 7.5\% under
steady-state operation. Previous studies with lower-fidelity models, including the two-equation
models, failed to capture this effect due to the time-averaging assumption required in those
models. After replacing the large inlet pipes with multiple blade-like inlet channels in the
\gls{MSFR} model, they managed to reduce power fluctuations to 1.2\%.
